Towards Verifying the Bitcoin-S Library

### 2019-06-22 paper/paper.tex
Added Reason of own library.
Added text to 2.4 about Stainless integration.

\todo{why does stainless use its own BigInt etc?}

In addition, Stainless has its own library with annotations,
reimplementation of some core data types, collections and input-output
functions and more.  Some of them are described on the website in the
section
\href{https://epfl-lara.github.io/stainless/library.html}{Stainless
  Library}.  There are more details about the library in the source
code of Stainless on GitHub \cite{Stainless:github} in the folder
\href{https://github.com/epfl-lara/stainless/tree/master/frontends/library/stainless}{\textit{frontends/library/stainless}}.

@@

\todo{anna: what does it mean to integrate}

Trying to integrate Stainless in Bitcoin-S caused a lot of troubles,
mainly because of version conflicts.  For more details see chapter
\ref{chap:appendix_arb}.

>>>>

In addition, Stainless has its own library with annotations,
reimplementation of some core data types, collections and input-output
functions and more. \todo{Kai: check the text.
This allows Stainless to map correctly operations 
to mathematical function inside of SMT solver.
Some elements of the library} are described on the website in the section
\href{https://epfl-lara.github.io/stainless/library.html}{Stainless
  Library}.  There are more details about the library in the source
code of Stainless on GitHub \cite{Stainless:github} in the folder
\href{https://github.com/epfl-lara/stainless/tree/master/frontends/library/stainless}{\textit{frontends/library/stainless}}.

@@

\todo{Kai: check the text
In order to verify a project, Stainless must be integrated into it.
We can integrate it in an sbt project adding the Stainless Plugin 
and the required resolver to pugins.sbt. 
Another option to use Stainless is to import its libraries in a program code 
and verify a program from command line using the pre-packaged Stainless JAR file 
or using the Stainless script built from source.}
Trying to integrate Stainless in Bitcoin-S caused a lot of troubles,
mainly because of version conflicts.  For more details see chapter
\ref{chap:appendix_arb}.
